### 2024-09-22 paper/paper.qmd
rename raw data

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

```

# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/analysis_data.csv")

# Ensure the date column is in the correct format (Month-Year format)
cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$date), format="%d-%b-%y")

# Filter to include only the "All Population" group
total_population_data <- subset(cleaned_shelter_data, group == "All Population")

# Load ggplot2 for plotting
ggplot(total_population_data, aes(x = date, y = homeless_count)) +
  geom_line(color = "blue", linewidth = 1.5) +  
  labs(title = "Total Homeless Population Over Time",
       x = "Date",
       y = "Homeless Population Count") +
  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-09-22 scripts/01-download_data.R
change file name

@@ -28,4 +28,4 @@ shelter_system_statistics
 
 #### Save data ####
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(shelter_system_statistics, "/Users/liz/Downloads/starter_folder-main/data/raw_data/shelter_raw_data.csv")
+write_csv(shelter_system_statistics, "/Users/liz/Downloads/starter_folder-main/data/raw_data/raw_data.csv")

### 2024-09-23 paper/paper.qmd
draw some graph

@@
 library(tidyverse)
+library(ggplot2)
+library(dplyr)
+library(scales) 
+library(tidyr)
 
@@
 
-cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/analysis_data.csv")
+cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
 
 # Ensure the date column is in the correct format (Month-Year format)
-cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$date), format="%d-%b-%y")
+cleaned_shelter_data$Date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
 
 # Filter to include only the "All Population" group
-total_population_data <- subset(cleaned_shelter_data, group == "All Population")
+total_population_data <- subset(cleaned_shelter_data, Population_Group == "All Population")
 
 # Load ggplot2 for plotting
-ggplot(total_population_data, aes(x = date, y = homeless_count)) +
-  geom_line(color = "blue", linewidth = 1.5) +  
+ggplot(total_population_data, aes(x = Date, y = Homeless_Count)) +
+  geom_line(color = "blue", linewidth = 1.5) +  # Adjust line color and width
   labs(title = "Total Homeless Population Over Time",
@@
        y = "Homeless Population Count") +
-  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  
+  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  # Show year on x-axis with 1-year intervals
   theme_minimal() +
@@
 ```{r}
+
+# Summarize data for all years (total homeless population by age group)
+total_data <- cleaned_shelter_data %>%
+  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
+            Age_16_24 = sum(Age_16_24, na.rm = TRUE),
+            Age_25_34 = sum(Age_25_34, na.rm = TRUE),
+            Age_35_44 = sum(Age_35_44, na.rm = TRUE),
+            Age_45_54 = sum(Age_45_54, na.rm = TRUE),
+            Age_55_64 = sum(Age_55_64, na.rm = TRUE),
+            Age_65_Over = sum(Age_65_Over, na.rm = TRUE))
+
+# Reshape data for plotting
+total_data_long <- tidyr::pivot_longer(total_data, 
+                                       cols = starts_with("Age"), 
+                                       names_to = "Age_Group", 
+                                       values_to = "Count")
+
+# Calculate percentages
+total_count <- sum(total_data_long$Count)
+total_data_long <- total_data_long %>%
+  mutate(Percent = round(Count / total_count * 100))
+
+# Create a pie chart with percentage labels
+ggplot(total_data_long, aes(x = "", y = Count, fill = Age_Group)) +
+  geom_bar(stat = "identity", width = 1) +
+  coord_polar("y") +
+  geom_text(aes(label = paste0(Percent, "%")), 
+            position = position_stack(vjust = 0.5), size = 4) +
+  labs(title = "Age Group Distribution of Total Homeless Population") +
+  theme_void() +
+  theme(legend.position = "right") +
+  scale_fill_brewer(palette = "Set3")  # Use a color palette for clarity
+
+```
+
+```{r}
+
+# Read the cleaned data
+cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
+
+# Ensure the date column is in the correct format
+cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
+cleaned_shelter_data$year <- format(cleaned_shelter_data$date, "%Y")  # Extract year as a string
+
+# Summarize data by year for different age groups
+age_data <- cleaned_shelter_data %>%
+  group_by(year) %>%
+  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
+            Age_16_24 = sum(Age_16_24, na.rm = TRUE),
+            Age_25_34 = sum(Age_25_34, na.rm = TRUE),
+            Age_35_44 = sum(Age_35_44, na.rm = TRUE),
+            Age_45_54 = sum(Age_45_54, na.rm = TRUE),
+            Age_55_64 = sum(Age_55_64, na.rm = TRUE),
+            Age_65_Over = sum(Age_65_Over, na.rm = TRUE))
+
+# Reshape data for plotting
+age_data_long <- pivot_longer(age_data, 
+                              cols = starts_with("Age"), 
+                              names_to = "Age_Group", 
+                              values_to = "Count")
+
+# Plot 100% stacked bar chart
+ggplot(age_data_long, aes(x = year, y = Count, fill = Age_Group)) +
+  geom_bar(stat = "identity", position = "fill") +  # Use 'fill' to normalize to 100%
+  scale_y_continuous(labels = percent) +  # Display percentages on y-axis
+  labs(title = "Age Group Proportion Over Time", 
+       x = "Year", y = "Proportion", fill = "Age Group") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set3")  # Use color palette for clarity
+
+```
+
+```{r}
 #| label: fig-planes
@@
 
-analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))
+# Read the cleaned data
+cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+# Ensure the date column is in the correct format
+cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
+cleaned_shelter_data$year <- as.numeric(format(cleaned_shelter_data$date, "%Y"))  # Extract year as numeric
+
+# Summarize data by year for different genders
+gender_data <- cleaned_shelter_data %>%
+  group_by(year) %>%
+  summarise(Male = sum(Male_Count, na.rm = TRUE),
+            Female = sum(Female_Count, na.rm = TRUE),
+            Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE))
+
+# Calculate total population for each year and for overall gender proportions
+total_population <- gender_data %>%
+  summarise(Male = sum(Male), Female = sum(Female), Non_Binary = sum(Non_Binary))
+
+# Calculate percentages for each gender over the entire period
+total_population_long <- pivot_longer(total_population, 
+                                      cols = c("Male", "Female", "Non_Binary"), 
+                                      names_to = "Gender", 
+                                      values_to = "Total_Count")
+
+# Calculate proportions
+total_population_long <- total_population_long %>%
+  mutate(Percent = round(Total_Count / sum(Total_Count) * 100, 1))
+
+# Create a string for the percentages to use in the legend
+gender_percentages <- paste0(total_population_long$Gender, " (", total_population_long$Percent, "%)")
+
+# Reshape data for plotting
+gender_data_long <- pivot_longer(gender_data, 
+                                 cols = c("Male", "Female", "Non_Binary"), 
+                                 names_to = "Gender", 
+                                 values_to = "Count")
+
+# Ensure gender order: Non-Binary at the bottom, Female in the middle, Male at the top
+gender_data_long$Gender <- factor(gender_data_long$Gender, levels = c("Non_Binary", "Female", "Male"))
+
+# Plot area chart with percentages in the legend
+ggplot(gender_data_long, aes(x = year, y = Count, fill = Gender)) +
+  geom_area(position = "stack") +
+  labs(title = "Homeless Population by Gender Over Time (Area Chart)", 
+       x = "Year", y = "Homeless Population Count", fill = "Gender") +
+  scale_fill_manual(values = c("Male" = "blue", "Female" = "pink", "Non_Binary" = "purple"),
+                    labels = gender_percentages) +  # Add percentages to the legend
+  theme_minimal()
+
 ```
@@
 Talk way more about it. 
+```{r}
 
-# Model
+# Summarize data by year for Chronic and All Population
+chronic_data <- cleaned_shelter_data %>%
+  filter(Population_Group == 'Chronic') %>%
+  group_by(year) %>%
+  summarize(homeless_count = sum(Homeless_Count))
 
-The goal of our modelling strategy is twofold. Firstly,...
+all_population_data <- cleaned_shelter_data %>%
+  filter(Population_Group == 'All Population') %>%
+  group_by(year) %>%
+  summarize(homeless_count = sum(Homeless_Count))
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+# Create Non-Chronic by subtracting Chronic from All Population
+non_chronic_data <- all_population_data
+non_chronic_data$homeless_count <- non_chronic_data$homeless_count - chronic_data$homeless_count
+non_chronic_data$group <- 'Non-Chronic'
 
-## Model set-up
+# Add Chronic to the dataset
+chronic_data$group <- 'Chronic'
+combined_data <- rbind(chronic_data, non_chronic_data)  # Combine data
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+# Ensure 'group' is a factor and order it so that Chronic appears at the top
+combined_data$group <- factor(combined_data$group, levels = c("Non-Chronic", "Chronic"))
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+# Reorder the data frame so that 'Non-Chronic' is plotted first (to appear at the bottom)
+combined_data <- combined_data %>%
+  arrange(group)
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+# Plot the stacked bar chart with Chronic at the top
+ggplot(combined_data, aes(x = year, y = homeless_count, fill = group)) +
+  geom_bar(stat = "identity", position = "stack") +
+  labs(title = "Chronic vs Non-Chronic Homeless Population by Year", 
+       x = "Year", y = "Homeless Population Count", fill = "Group") +
+  theme_minimal() +
+  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange"))  # Adjust colors if needed
+
+```
 

### 2024-09-23 paper/paper.qmd
add some information of the graph

@@
 author: 
-  - First author
+  - Jianing Li
   - Another author
@@
 # Data {#sec-data}
-
+## Overview {#sec-data-overview}
 Some of our data is of penguins (@fig-bills), from @palmerpenguins.
 
+## Results {#sec-data-results}
+
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
 #| echo: false
+#| warning: false
+#| label: fig-total-population
+#| fig-cap: "Trend of Homeless Population in Toronto from 2018 to 2024"
 
@@
   geom_line(color = "blue", linewidth = 1.5) +  # Adjust line color and width
-  labs(title = "Total Homeless Population Over Time",
-       x = "Date",
+  labs(x = "Date",
        y = "Homeless Population Count") +
-  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  # Show year on x-axis with 1-year intervals
+  scale_x_date(date_labels = "%Y", date_breaks = "1 year") +  
   theme_minimal() +
@@
 
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+@fig-total-population illustrates the fluctuation in Toronto's homeless population from 2018 to 2024.
+The chart shows cyclical rises and falls, with more pronounced declines around 2020 and 2021, followed by a steady recovery.
+The population reaches its highest point in 2024.
+Throughout this period, the homeless population varies between approximately 7,500 and 11,000 individuals.
 
 ```{r}
+#| echo: false
+#| warning: false
+#| label: fig-age-distribution
+#| fig-cap: "Age Group Distribution of Homeless Population in Toronto (2018-2024)"
 
@@
             position = position_stack(vjust = 0.5), size = 4) +
-  labs(title = "Age Group Distribution of Total Homeless Population") +
   theme_void() +
@@
 ```
+@fig-age-distribution shows the percentage of Toronto's homeless population in each age group as a proportion of the total homeless population from 2018 to 2024.
+The largest age group is 35-44 years old, accounting for about 21\% of the total population, followed by the 25-34 age group (approximately 18\%), the 45-54 age group (approximately 17\%), and the 55-64 age group (approximately 14\%).
+The under 16 and 16-24 age groups each account for 12\%.
+The smallest age group is 65 years and above, making up about 7\% of the total population.
 
 ```{r}
-
-# Read the cleaned data
-cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
-
-# Ensure the date column is in the correct format
-cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
-cleaned_shelter_data$year <- format(cleaned_shelter_data$date, "%Y")  # Extract year as a string
-
-# Summarize data by year for different age groups
-age_data <- cleaned_shelter_data %>%
-  group_by(year) %>%
-  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
-            Age_16_24 = sum(Age_16_24, na.rm = TRUE),
-            Age_25_34 = sum(Age_25_34, na.rm = TRUE),
-            Age_35_44 = sum(Age_35_44, na.rm = TRUE),
-            Age_45_54 = sum(Age_45_54, na.rm = TRUE),
-            Age_55_64 = sum(Age_55_64, na.rm = TRUE),
-            Age_65_Over = sum(Age_65_Over, na.rm = TRUE))
-
-# Reshape data for plotting
-age_data_long <- pivot_longer(age_data, 
-                              cols = starts_with("Age"), 
-                              names_to = "Age_Group", 
-                              values_to = "Count")
-
-# Plot 100% stacked bar chart
-ggplot(age_data_long, aes(x = year, y = Count, fill = Age_Group)) +
-  geom_bar(stat = "identity", position = "fill") +  # Use 'fill' to normalize to 100%
-  scale_y_continuous(labels = percent) +  # Display percentages on y-axis
-  labs(title = "Age Group Proportion Over Time", 
-       x = "Year", y = "Proportion", fill = "Age Group") +
-  theme_minimal() +
-  scale_fill_brewer(palette = "Set3")  # Use color palette for clarity
-
-```
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
 #| echo: false
 #| warning: false
-#| message: false
-
+#| label: fig-gender-distribution
+#| fig-cap: "Homeless Population by Gender in Toronto (2018-2024)"
+#| 
 # Read the cleaned data
@@
   geom_area(position = "stack") +
-  labs(title = "Homeless Population by Gender Over Time (Area Chart)", 
-       x = "Year", y = "Homeless Population Count", fill = "Gender") +
+  labs(x = "Year", y = "Homeless Population Count", fill = "Gender") +
   scale_fill_manual(values = c("Male" = "blue", "Female" = "pink", "Non_Binary" = "purple"),
@@
 
-Talk way more about it. 
+@fig-gender-distribution presents the gender distribution of Toronto's homeless population from 2018 to 2024.
+During this period, males have consistently made up the largest proportion, accounting for approximately 61.8% of the total homeless population.
+Females make up about 36.8%, while non-binary individuals make up about 1.4%.
+Over time, the total homeless population of each gender has shown similar trends, meaning that the proportion of each gender has remained almost constant.
+
 ```{r}
+#| echo: false
+#| warning: false
+#| label: fig-chronic-population
+#| fig-cap: "Comparison of Chronic vs Non-Chronic Homeless Population in Toronto (2019-2024)"
 
@@
   geom_bar(stat = "identity", position = "stack") +
-  labs(title = "Chronic vs Non-Chronic Homeless Population by Year", 
-       x = "Year", y = "Homeless Population Count", fill = "Group") +
+  labs(x = "Year", y = "Homeless Population Count", fill = "Group") +
   theme_minimal() +
@@
 
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
 # Results
@@
 Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
-```
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
-## Diagnostics
-
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
-
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
-
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
-\newpage
-
 # References

### 2024-09-23 paper/paper.qmd
add a reference

@@
 total_population_long <- pivot_longer(total_population, 
-                                      cols = c("Male", "Female", "Non_Binary"), 
+                                      cols = c("Non_Binary", "Female", "Male"), 
                                       names_to = "Gender", 
@@
 
-# Ensure gender order: Non-Binary at the bottom, Female in the middle, Male at the top
 gender_data_long$Gender <- factor(gender_data_long$Gender, levels = c("Non_Binary", "Female", "Male"))
@@
 #| label: fig-chronic-population
-#| fig-cap: "Comparison of Chronic vs Non-Chronic Homeless Population in Toronto (2019-2024)"
+#| fig-cap: "Changes in Chronic and Non-Chronic Homeless Population and Proportion in Toronto (2018-2024)"
 
@@
 
-# Reorder the data frame so that 'Non-Chronic' is plotted first (to appear at the bottom)
-combined_data <- combined_data %>%
-  arrange(group)
+# Calculate the proportion of Chronic for each year
+proportions <- chronic_data %>%
+  left_join(all_population_data, by = "year", suffix = c("_chronic", "_all")) %>%
+  mutate(percentage = round((homeless_count_chronic / homeless_count_all) * 100, 1))
 
-# Plot the stacked bar chart with Chronic at the top
+# Plot the stacked bar chart with Chronic at the top and add percentages
 ggplot(combined_data, aes(x = year, y = homeless_count, fill = group)) +
   geom_bar(stat = "identity", position = "stack") +
+  geom_text(data = proportions, aes(x = year, y = homeless_count_chronic, label = paste0(percentage, "%")),
+            vjust = 1.5, color = "white", size = 4) +  # Add percentage labels in white color
   labs(x = "Year", y = "Homeless Population Count", fill = "Group") +
   theme_minimal() +
-  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange"))  # Adjust colors if needed
+  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange"))
 
@@
 
-# Results
-
-Our results are summarized in @tbl-modelresults.
+The @chronic-population displays the changes in the number and proportion of chronic and non-chronic homeless people in Toronto between 2018 and 2024.
+The number of chronically homeless has been growing over this time, with over 30,000 people in 2018, and by 2023, the number has gone to about 60,000, nearly doubling.
+the slight drop in numbers in 2024 is due to the fact that the statistics were last updated on September 17, 2024, and it is projected that by the end of the year, the number will have exceeded the 2023 one.
+Similarly, the percentage of chronically homeless is growing every year, from 29.7% in 2019 to 63.7% in 2024.
+Note that in 2019 to 2020 and 2023 to 2024, the rate grows faster, by about 10 percent.
 

### 2024-09-24 paper/paper.qmd
write Discussion in paper and add some reference

@@
 library(dplyr)
-library(scales) 
 library(tidyr)
@@
 ## Overview {#sec-data-overview}
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+The dataset used for this analysis is the “Toronto Shelter System Flows” dataset from the Toronto Open Data Platform [@torontosheltersystem].
+It shows the total number of homeless people entering and exiting shelters each month from 2018 to September 2024, as well as the number of different age groups and genders.
+It also shows the number and proportion of chronic homeless, refugees, youth, single adults, and families in the total homeless population.
+These data are updated monthly and reflect the latest trends in Toronto's homeless population and shelter system[@torontosheltersystem].
+
+The variables of interest in this analysis vary by age group (Under 16, 16-24, 25-34, 35-44, 45-54, 55-64, 65 and over) and gender (Male, Female, Transgender/Non-Binary), as well as Chronic and All populations.
+According to @torontosheltersystem, Chronic refers to those who, according to the federal government's definition of chronic homelessness, meet one of the following two criteria: first, stayed in a shelter for at least 180 nights in the past year; and second, stayed in a shelter multiple times in the past three years, totaling at least 546 cumulative nights.
+All populations refers to the total number of homeless persons covered in the report without any demographic breakdown.
+
+Similar datasets available on the City of Toronto's Open Data Catalogue include Daily Shelter & Overnight Service Occupancy & Capacity and Daily Shelter Occupancy[@opendata].
+However, these datasets only provide an overview of shelter usage without categorizing the homeless population using the shelters.
+As a result, they were not used in this analysis.
 
 ## Results {#sec-data-results}
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+# Loading the Cleaned Dataset #
+cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
+
+# Generated by ChatGPT
+cleaned_shelter_data$Date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
+cleaned_shelter_data$year <- as.numeric(format(cleaned_shelter_data$Date, "%Y"))
+
+```
 
@@
 
-cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
-
-# Ensure the date column is in the correct format (Month-Year format)
-cleaned_shelter_data$Date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
-
 # Filter to include only the "All Population" group
@@
 
+# This code is based on knowledge from Alexander (2023).
 # Load ggplot2 for plotting
 ggplot(total_population_data, aes(x = Date, y = Homeless_Count)) +
-  geom_line(color = "blue", linewidth = 1.5) +  # Adjust line color and width
+  geom_line(color = "blue", linewidth = 1.5) +  
   labs(x = "Date",
@@
 @fig-total-population illustrates the fluctuation in Toronto's homeless population from 2018 to 2024.
-The chart shows cyclical rises and falls, with more pronounced declines around 2020 and 2021, followed by a steady recovery.
-The population reaches its highest point in 2024.
+The chart shows cyclical rises and falls, with more pronounced declines around 2020 and 2021, followed by a steady increase.The population reaches its highest point in 2024.
 Throughout this period, the homeless population varies between approximately 7,500 and 11,000 individuals.
@@
 # Summarize data for all years (total homeless population by age group)
+# Generated by ChatGPT
 total_data <- cleaned_shelter_data %>%
@@
 # Reshape data for plotting
+# Generated by ChatGPT
 total_data_long <- tidyr::pivot_longer(total_data, 
@@
 # Calculate percentages
+# Generated by ChatGPT
 total_count <- sum(total_data_long$Count)
@@
 # Create a pie chart with percentage labels
+# This code is based on knowledge from Alexander (2023) and further refined using the RStudio Help documentation.
 ggplot(total_data_long, aes(x = "", y = Count, fill = Age_Group)) +
@@
   theme(legend.position = "right") +
-  scale_fill_brewer(palette = "Set3")  # Use a color palette for clarity
+  scale_fill_brewer(palette = "Set3")
 
@@
 #| 
-# Read the cleaned data
-cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
-
-# Ensure the date column is in the correct format
-cleaned_shelter_data$date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
-cleaned_shelter_data$year <- as.numeric(format(cleaned_shelter_data$date, "%Y"))  # Extract year as numeric
-
 # Summarize data by year for different genders
+# This logic is similar to the previous graph of age group 
 gender_data <- cleaned_shelter_data %>%
@@
             Female = sum(Female_Count, na.rm = TRUE),
-            Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE))
+            Other = sum(Transgender_Non_Binary_Count, na.rm = TRUE))
 
-# Calculate total population for each year and for overall gender proportions
+# Calculate total population for each gender over the entire period
 total_population <- gender_data %>%
-  summarise(Male = sum(Male), Female = sum(Female), Non_Binary = sum(Non_Binary))
+  summarise(Male = sum(Male), Female = sum(Female), Other = sum(Other))
 
-# Calculate percentages for each gender over the entire period
+# Reshape data for plotting
 total_population_long <- pivot_longer(total_population, 
-                                      cols = c("Non_Binary", "Female", "Male"), 
+                                      cols = c("Other", "Female", "Male"), 
                                       names_to = "Gender", 
@@
 
-# Calculate proportions
+# Calculate percentages for each gender
 total_population_long <- total_population_long %>%
@@
 
-# Create a string for the percentages to use in the legend
-gender_percentages <- paste0(total_population_long$Gender, " (", total_population_long$Percent, "%)")
-
-# Reshape data for plotting
-gender_data_long <- pivot_longer(gender_data, 
-                                 cols = c("Male", "Female", "Non_Binary"), 
-                                 names_to = "Gender", 
-                                 values_to = "Count")
-
-gender_data_long$Gender <- factor(gender_data_long$Gender, levels = c("Non_Binary", "Female", "Male"))
-
-# Plot area chart with percentages in the legend
-ggplot(gender_data_long, aes(x = year, y = Count, fill = Gender)) +
-  geom_area(position = "stack") +
-  labs(x = "Year", y = "Homeless Population Count", fill = "Gender") +
-  scale_fill_manual(values = c("Male" = "blue", "Female" = "pink", "Non_Binary" = "purple"),
-                    labels = gender_percentages) +  # Add percentages to the legend
-  theme_minimal()
+# Create a pie chart similar to the one used for age groups
+# This code is based on knowledge from Alexander (2023) and further refined using the RStudio Help documentation.
+ggplot(total_population_long, aes(x = "", y = Total_Count, fill = Gender)) +
+  geom_bar(stat = "identity", width = 1) +
+  coord_polar("y") +
+  geom_text(aes(label = paste0(Percent, "%")), 
+            position = position_stack(vjust = 0.5), size = 4, fontface = "bold", color = "gray30") +  
+  theme_void() +
+  theme(legend.position = "right") +
+  scale_fill_manual(values = c("Male" = "#7FB3D5", "Female" = "#F5B7B1", "Other" = "#D2B4DE"))
 
@@
 Females make up about 36.8%, while non-binary individuals make up about 1.4%.
-Over time, the total homeless population of each gender has shown similar trends, meaning that the proportion of each gender has remained almost constant.
 
@@
 # Summarize data by year for Chronic and All Population
+# Generated by ChatGPT
 chronic_data <- cleaned_shelter_data %>%
@@
   geom_text(data = proportions, aes(x = year, y = homeless_count_chronic, label = paste0(percentage, "%")),
-            vjust = 1.5, color = "white", size = 4) +  # Add percentage labels in white color
+            vjust = 1.5, color = "white", size = 3) +  # Add percentage labels in white color
   labs(x = "Year", y = "Homeless Population Count", fill = "Group") +
@@
 
-The @chronic-population displays the changes in the number and proportion of chronic and non-chronic homeless people in Toronto between 2018 and 2024.
+The @fig-chronic-population displays the changes in the number and proportion of chronic and non-chronic homeless people in Toronto between 2018 and 2024.
 The number of chronically homeless has been growing over this time, with over 30,000 people in 2018, and by 2023, the number has gone to about 60,000, nearly doubling.
@@
 
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-## Third discussion point
+## Overview of Homeless Trends (2018-2024)
+In @sec-data-results，trends in Toronto's homeless population from 2018 to 2024 are presented, focusing on key factors such as age, gender, and chronic versus non-chronic conditions.
+The homeless population fluctuates significantly, being significantly impacted in specific years such as 2020 and 2021[@fig-total-population], with males and the 35-44 age group making up the majority of the homeless population[@fig-age-distribution,@fig-gender-distribution], and chronic homelessness showing an increasing trend[@fig-chronic-population].
+## Impact of COVID-19 on Homelessness
+The homeless population declined significantly in 2020 and 2021, likely due to COVID-19.
+To meet social distancing requirements, the Toronto government reduced shelter capacity and opened temporary shelters, including additional spaces in hotels and motels[@may2023scan].
+These actions may explain the drop during these years.
+However, the rebound in homelessness afterward suggests that issues like housing affordability and lack of social support remain unresolved, highlighting the need for sustainable long-term solutions.
+## Demographic and Chronic Homelessness Insights
+An analysis of age, gender, and chronic homelessness provides key insights into Toronto's homeless population.
+Homelessness is concentrated among working-age adults, especially those aged 35-44 and 25-34, likely due to challenges with employment or housing stability.
+In terms of gender, males consistently make up the majority, while non-binary individuals account for only 1.4%.
+This suggests shelters should consider different designs for men and women, while also addressing the needs of non-binary individuals, despite their smaller numbers.
+The rise in chronic homelessness suggests that existing measures are not enough to help people exit homelessness permanently.
 
@@
 
-# Model details {#sec-model-details}
-
 ## Posterior predictive check

### 2024-09-24 paper/paper.qmd
add "weakness"; aad personal information

@@
   - Jianing Li
-  - Another author
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/JianingLi1225/Toronto_Homeless.git."
 date: today
@@
 #| message: false
-
+#### Workspace setup ####
 library(tidyverse)
@@
 # Introduction
-
-You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.
-
-The remainder of this paper is structured as follows. @sec-data....
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 ## Weaknesses and next steps
+A limitation of this analysis is that the data analyzed does not reflect the entire Toronto homeless population.
+The database used only includes people who use City of Toronto-funded overnight shelter services and fails to reflect people who spend the night outdoors or use other homeless services.
+According to the most recent Street Needs Assessment, approximately 18% of the homeless population is not included in the data[@torontosheltersystem].
 
-Weaknesses and next steps should also be included.
+Future directions for improvement should include expanding the data scope of the analysis to include people who spend the night outdoors and use shelters that are not funded by the Government of Toronto, in order to provide a more complete picture of homelessness in Toronto.
+This will help fill data gaps and support more effective policy decisions.
 
@@
 
-## Posterior predictive check
-
 # References

### 2024-09-24 scripts/00-simulate_data.R

@@ -1,19 +1,61 @@
 #### Preamble ####
-# Purpose: Simulates... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Generates a simulated version of the Toronto Shelter System dataset
+# Author: Jianing Li
+# Date: September 23, 2024
+# Contact: lijianing.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: Install the tidyverse (Wickham et al. 2019) package.
+# Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+# Set random seed to ensure reproducibility
+set.seed(500)
 
+# Simulate a date column from January 2018 to August 2024, monthly
+# Generated by ChatGPT
+dates <- seq(as.Date("2018-01-01"), as.Date("2024-08-01"), by = "month")
 
+# Simulate population groups
+population_groups <- c("Chronic", "All populations")
+
+# Generate random homeless counts
+homeless_count <- sample(1000:3000, length(dates) * length(population_groups), replace = TRUE)
+
+# Generate random age group counts
+age_under_16 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+age_16_24 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+age_25_34 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+age_35_44 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+age_45_54 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+age_55_64 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+age_65_over <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+
+# Generate random gender counts
+male_count <- sample(500:1500, length(dates) * length(population_groups), replace = TRUE)
+female_count <- sample(500:1500, length(dates) * length(population_groups), replace = TRUE)
[…]

### 2024-09-24 scripts/01-download_data.R

@@ -1,16 +1,21 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
+# Purpose: Downloads the data from the opendatatoronto package (Gelfand 2022)
+# and saves the dataset.
 # Author: Jianing Li
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Date: September 23, 2024
+# Contact: lijianing.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Install the opendatatoronto (Gelfand 2022) and
+# tidyverse (Wickham et al. 2019) packages.
+# Any other information needed? None
 
 
 #### Workspace setup ####
+# install.packages("opendatatoronto")
+# install.packages("tidyverse")
 library(opendatatoronto)
 library(tidyverse)
+
 packages <- list_packages(500)
 packages
 
@@ -27,5 +32,5 @@ shelter_system_statistics <- shelter_system_resources[2, ] %>%
 shelter_system_statistics
 
 #### Save data ####
-# change the_raw_data to whatever name you assigned when you downloaded it.
+
 write_csv(shelter_system_statistics, "/Users/liz/Downloads/starter_folder-main/data/raw_data/raw_data.csv")

### 2024-09-24 scripts/02-data_cleaning.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
+# Purpose: Cleans the raw dataset obtained from the 
+#"Toronto Shelter System Flow" dataset in the file "01-download_data.R".
 # Author: Jianing Li
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Date: September 23, 2024
+# Contact: lijianing.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: Run the file "01-download_data.R".
+# Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-09-24 scripts/03-test_data.R

@@ -1,15 +1,98 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the validity of the simulated dataset.
+# Author: Jianing Li
+# Date: September 23, 2024
+# Contact: lijianing.li@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: Simulated dataset from "00-simulate_data.R".
+# Any other information needed? None
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Test data ####
+# Load the dataset
+simulated_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/raw_data/simulated_shelter_data.csv")
+
+# Check the structure of the dataset
+# Generated by ChatGPT
+str(simulated_data)
+
+# Check the first few rows of the data to ensure it loaded correctly
+head(simulated_data)
+
+# Test for missing values
+any_na <- any(is.na(simulated_data))
+if (any_na) {
+  print("There are missing values in the dataset.")
+} else {
+  print("No missing values in the dataset.")
+}
+
+# Check the range of homeless counts
+range_homeless <- range(simulated_data$Homeless_Count)
+if (range_homeless[1] >= 1000 & range_homeless[2] <= 3000) {
+  print("Homeless_Count is within the expected range (1000 to 3000).")
+} else {
+  print("Homeless_Count is outside the expected range.")
+}
+
+# Check the range of age groups
+range_age_16_24 <- range(simulated_data$Age_16_24)
+if (range_age_16_24[1] >= 100 & range_age_16_24[2] <= 500) {
+  print("Age_16_24 is within the expected range (100 to 500).")
+} else {
+  print("Age_16_24 is outside the expected range.")
+}
+
+# Check the range of Male_Count
+range_male <- range(simulated_data$Male_Count)
+if (range_male[1] >= 500 & range_male[2] <= 1500) {
+  print("Male_Count is within the expected range (500 to 1500).")
+} else {
+  print("Male_Count is outside the expected range.")
+}
+
+# Check the range of Female_Count
+range_female <- range(simulated_data$Female_Count)
[…]

### 2024-09-24 paper/paper.qmd
write the introduction

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Trends and Challenges in Toronto’s Homeless Population (2018-2024)"
+subtitle: "A Focus on Demographics and Chronic Homelessness"
 author: 
   - Jianing Li
-thanks: "Code and data are available at: https://github.com/JianingLi1225/Toronto_Homeless.git."
+thanks: "Code and data are available at: https://github.com/JianingLi1225/Toronto_Homeless"
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper explores Toronto’s homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness trends.
+The data reveal a decline during the pandemic, followed by a rebound, with males and individuals aged 35-44 making up the majority.
+The number of chronically homeless also increased significantly.
+These findings highlight the need for targeted interventions to address chronic homelessness and improve housing policies."
 format: pdf
@@
 library(tidyr)
-
 ```
@@
 
+Homelessness is a growing global concern, especially with rapid urbanization and the housing crisis.
+As Canada's largest city, Toronto faces a growing homeless population[@toronto2024].
+In addition to being a socio-economic issue, homelessness intersects with public health and social justice[@healthhomelessness].
+Understanding the trends and composition of the homeless population is critical to effective policymaking.
+However, existing data often lack detailed categorization, hindering a full understanding of the needs of specific groups.
+This study seeks to fill this gap.
+
+Using the "Toronto Shelter System Flows" dataset form Toronto Open Data Platform[@torontosheltersystem], this paper examines trends in Toronto's homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness.
+Our analysis reveals a decline during the pandemic, followed by a rebound, with males and the 35-44 age group comprising the majority.
+The number of chronically homeless people continues to grow, providing important insights for policymakers.
+
+In this essay, the (@sec-data-overview) section explains the background and necessity of using this dataset, followed by an explanation of the variables mentioned and the methods used.
+The (@sec-data-results) section shows the changes in the number of homeless population and the proportion of each age group, gender and chronic homelessness.
+Graphs and related explanations are provided.
+The (@sec-discussion) section further analyses the information presented in the graphs.
+
 # Data {#sec-data}
 ## Overview {#sec-data-overview}
+
 The dataset used for this analysis is the “Toronto Shelter System Flows” dataset from the Toronto Open Data Platform [@torontosheltersystem].
-It shows the total number of homeless people entering and exiting shelters each month from 2018 to September 2024, as well as the number of different age groups and genders.
+Similar datasets available on the City of Toronto's Open Data Catalogue include Daily Shelter & Overnight Service Occupancy & Capacity and Daily Shelter Occupancy[@opendata].
+However, these datasets only provide an overview of shelter usage without categorizing the homeless population using the shelters.
+As a result, they were not used in this analysis.
+
+This dataset shows the total number of homeless people entering and exiting shelters each month from 2018 to September 2024, as well as the number of different age groups and genders.
 It also shows the number and proportion of chronic homeless, refugees, youth, single adults, and families in the total homeless population.
@@
 
-Similar datasets available on the City of Toronto's Open Data Catalogue include Daily Shelter & Overnight Service Occupancy & Capacity and Daily Shelter Occupancy[@opendata].
-However, these datasets only provide an overview of shelter usage without categorizing the homeless population using the shelters.
-As a result, they were not used in this analysis.
+All processes are performed through the R language[@citeR].
+Data is simulated and tested using the `tidyverse`[@tidyverse] packages , and data is downloaded through the `tidyverse`[@tidyverse] and `opendatatoronto`[@citeopendatatorontoR] packages.
+The `tidyverse`[@tidyverse] packages are also used for data cleaning, removing unneeded variables and renaming variables.
+In addition to these parcels mentioned, the `ggplot2`[@ggplot2], `dplyr`[@dplyr] and `tidyr`[@tidyr] packages are used when plotting the graphs.
 
@@
 # Loading the Cleaned Dataset #
-cleaned_shelter_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
+cleaned_shelter_data <- read_csv(here::here("data", "analysis_data", "shelter_analysis_data.csv"))
 
@@
 ```
+
+In this section, the dataset is first loaded in the R programming language[@citeR] and the dates in the data are converted into a suitable format.
+Then, the change in the total homeless population over time, the percentage of each age group and gender and the change in the number and percentage of chronic homeless population over time were presented in the form of graphs.
+The `ggplot2` [@ggplot2], `dplyr` [@dplyr] and `tidyr` [@tidyr] packages were utilised in drawing the graphs in the R programming language, and the code was done with the help of Chatgpt, which is also referred to @Rohan.
 
@@
   theme_minimal() +
-  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange"))
+  scale_fill_manual(values = c("Chronic" = "blue", "Non-Chronic" = "orange")) +
+  scale_x_continuous(breaks = seq(min(combined_data$year), max(combined_data$year), by = 1))
 
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
 # References

### 2024-09-24 scripts/02-data_cleaning.R
cleaning data（remove some information)

@@ -12,18 +12,17 @@
 library(tidyverse)
 
 # Read the data
-cleaned_shelter_data <- read_csv("/Users/liz/Downloads/starter_folder-main/data/raw_data/shelter_raw_data.csv") %>%
+cleaned_shelter_data <- read_csv("/Users/liz/Downloads/starter_folder-main/data/raw_data/raw_data.csv") %>%
   
   # Filter data to keep only 'All Population' and 'Chronic' rows
   filter(population_group %in% c('All Population', 'Chronic')) %>%
   
   # Remove unnecessary columns
   select(-returned_from_housing, -returned_to_shelter, -newly_identified, 
-         -moved_to_housing, -became_inactive) %>%
+         -moved_to_housing, -became_inactive, -population_group_percentage, -X_id) %>%
   
   # Rename columns
   rename(
-    ID = X_id,
     Date = date.mmm.yy.,
     Population_Group = population_group,
     Homeless_Count = actively_homeless,
@@ -36,10 +35,7 @@ cleaned_shelter_data <- read_csv("/Users/liz/Downloads/starter_folder-main/data/
     Age_65_Over = age65over,
     Male_Count = gender_male,
     Female_Count = gender_female,
-    Transgender_Non_Binary_Count = gender_transgender.non.binary_or_two_spirit,
-    Population_Group_Percentage = population_group_percentage)
-
+    Transgender_Non_Binary_Count = gender_transgender.non.binary_or_two_spirit)
 
 #### Save data ####
-write_csv(cleaned_shelter_data, "/Users/liz/Downloads/starter_folder-main/data/analysis_data/shelter_analysis_data.csv")
-
+write_csv(cleaned_shelter_data, "/Users/liz/Downloads/starter_folder-main/data/analysis_data/analysis_data.csv")

### 2024-09-25 paper/paper.qmd
cleaning data（remove some information)
add sketcht

@@
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 
-In this essay, the (@sec-data-overview) section explains the background and necessity of using this dataset, followed by an explanation of the variables mentioned and the methods used.
-The (@sec-data-results) section shows the changes in the number of homeless population and the proportion of each age group, gender and chronic homelessness.
+In this essay, @sec-data-overview explains the background and necessity of using this dataset, followed by an explanation of the variables mentioned and the methods used.
+@sec-data-results shows the changes in the number of homeless population and the proportion of each age group, gender and chronic homelessness.
 Graphs and related explanations are provided.
-The (@sec-discussion) section further analyses the information presented in the graphs.
+@sec-discussion further analyses the information presented in the graphs.
 
@@
 # Loading the Cleaned Dataset #
-cleaned_shelter_data <- read_csv(here::here("data", "analysis_data", "shelter_analysis_data.csv"))
+cleaned_shelter_data <- read_csv(here::here("data", "analysis_data", "analysis_data.csv"))
 
@@
 
-# This code is based on knowledge from Alexander (2023).
+# This code draws on concepts from Alexander (2023)
 # Load ggplot2 for plotting
@@
 # Create a pie chart with percentage labels
-# This code is based on knowledge from Alexander (2023) and further refined using the RStudio Help documentation.
+# This code draws on concepts from Alexander (2023)
 ggplot(total_data_long, aes(x = "", y = Count, fill = Age_Group)) +
@@
             Female = sum(Female_Count, na.rm = TRUE),
-            Other = sum(Transgender_Non_Binary_Count, na.rm = TRUE))
+            Transgender_Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE))  # Change 'Other' to 'Transgender/Non-binary'
 
@@
 total_population <- gender_data %>%
-  summarise(Male = sum(Male), Female = sum(Female), Other = sum(Other))
+  summarise(Male = sum(Male), Female = sum(Female), Transgender_Non_Binary = sum(Transgender_Non_Binary))  # Adjust for renamed column
 
-# Reshape data for plotting
+# Reshape data for plotting and update Transgender_Non_Binary to Transgender/Non-binary
 total_population_long <- pivot_longer(total_population, 
-                                      cols = c("Other", "Female", "Male"), 
+                                      cols = c("Transgender_Non_Binary", "Female", "Male"), 
                                       names_to = "Gender", 
-                                      values_to = "Total_Count")
+                                      values_to = "Total_Count") %>%
+  mutate(Gender = recode(Gender, "Transgender_Non_Binary" = "Transgender/Non-binary"))  # Replace underscore with /
 
@@
   theme(legend.position = "right") +
-  scale_fill_manual(values = c("Male" = "#7FB3D5", "Female" = "#F5B7B1", "Other" = "#D2B4DE"))
-
+  scale_fill_manual(values = c("Male" = "#7FB3D5", "Female" = "#F5B7B1", "Transgender/Non-binary" = "#D2B4DE"))  
 ```
@@
 The homeless population fluctuates significantly, being significantly impacted in specific years such as 2020 and 2021[@fig-total-population], with males and the 35-44 age group making up the majority of the homeless population[@fig-age-distribution,@fig-gender-distribution], and chronic homelessness showing an increasing trend[@fig-chronic-population].
+
 ## Impact of COVID-19 on Homelessness
@@
 However, the rebound in homelessness afterward suggests that issues like housing affordability and lack of social support remain unresolved, highlighting the need for sustainable long-term solutions.
+
 ## Demographic and Chronic Homelessness Insights

### 2024-09-26 paper/paper.qmd
Update some graph

@@
 Homelessness is a growing global concern, especially with rapid urbanization and the housing crisis.
-As Canada's largest city, Toronto faces a growing homeless population[@toronto2024].
-In addition to being a socio-economic issue, homelessness intersects with public health and social justice[@healthhomelessness].
+As Canada's largest city, Toronto faces a growing homeless population [@toronto2024].
+In addition to being a socio-economic issue, homelessness intersects with public health and social justice [@healthhomelessness].
 Understanding the trends and composition of the homeless population is critical to effective policymaking.
@@
 
-Using the "Toronto Shelter System Flows" dataset form Toronto Open Data Platform[@torontosheltersystem], this paper examines trends in Toronto's homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness.
+Using the "Toronto Shelter System Flows" dataset form Toronto Open Data Platform [@torontosheltersystem], this paper examines trends in Toronto's homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness.
 Our analysis reveals a decline during the pandemic, followed by a rebound, with males and the 35-44 age group comprising the majority.
@@
 In this essay, @sec-data-overview explains the background and necessity of using this dataset, followed by an explanation of the variables mentioned and the methods used.
-@sec-data-results shows the changes in the number of homeless population and the proportion of each age group, gender and chronic homelessness.
+@sec-data-results shows the changes in the number of homeless individuals, along with the proportions and trends over time for each age group, gender, and chronic homelessness.
 Graphs and related explanations are provided.
@@
 The dataset used for this analysis is the “Toronto Shelter System Flows” dataset from the Toronto Open Data Platform [@torontosheltersystem].
-Similar datasets available on the City of Toronto's Open Data Catalogue include Daily Shelter & Overnight Service Occupancy & Capacity and Daily Shelter Occupancy[@opendata].
-However, these datasets only provide an overview of shelter usage without categorizing the homeless population using the shelters.
-As a result, they were not used in this analysis.
-
-This dataset shows the total number of homeless people entering and exiting shelters each month from 2018 to September 2024, as well as the number of different age groups and genders.
-It also shows the number and proportion of chronic homeless, refugees, youth, single adults, and families in the total homeless population.
-These data are updated monthly and reflect the latest trends in Toronto's homeless population and shelter system[@torontosheltersystem].
+It focuses on the measurement of homeless individuals' flow within Toronto’s shelter system, which is funded and operated by the City of Toronto.
+It covers data from 2018 to September 2024, with the homeless count based on shelter admission records, including demographic information such as age and gender.
+The dataset also provides data on specific groups, including chronic homeless individuals, refugees, youth, single adults, and families.
+The measurements are collected through the Shelter Management Information System (SMIS) and are updated monthly to ensure that trends in the homeless population are accurately and timely reflected [@torontosheltersystem].
 
@@
 
-All processes are performed through the R language[@citeR].
-Data is simulated and tested using the `tidyverse`[@tidyverse] packages , and data is downloaded through the `tidyverse`[@tidyverse] and `opendatatoronto`[@citeopendatatorontoR] packages.
-The `tidyverse`[@tidyverse] packages are also used for data cleaning, removing unneeded variables and renaming variables.
-In addition to these parcels mentioned, the `ggplot2`[@ggplot2], `dplyr`[@dplyr] and `tidyr`[@tidyr] packages are used when plotting the graphs.
+Similar datasets available on the City of Toronto's Open Data Catalogue include Daily Shelter & Overnight Service Occupancy & Capacity and Daily Shelter Occupancy [@opendata].
+However, these datasets only provide an overview of shelter usage without categorizing the homeless population using the shelters.
+As a result, they were not used in this analysis.
+
+All processes are performed through the `R` language [@citeR].
+Data is simulated, tested, and cleaned using the `tidyverse` [@tidyverse] packages, which also facilitate downloading data through `opendatatoronto` [@citeopendatatorontoR].
+Unneeded variables are removed and renamed using `dplyr` [@dplyr] and `tidyr` [@tidyr], while graphs are plotted with `ggplot2` [@ggplot2].
 
@@
 # Loading the Cleaned Dataset #
+# Generated by ChatGPT
 cleaned_shelter_data <- read_csv(here::here("data", "analysis_data", "analysis_data.csv"))
@@
 
-In this section, the dataset is first loaded in the R programming language[@citeR] and the dates in the data are converted into a suitable format.
-Then, the change in the total homeless population over time, the percentage of each age group and gender and the change in the number and percentage of chronic homeless population over time were presented in the form of graphs.
-The `ggplot2` [@ggplot2], `dplyr` [@dplyr] and `tidyr` [@tidyr] packages were utilised in drawing the graphs in the R programming language, and the code was done with the help of Chatgpt, which is also referred to @Rohan.
+In this section, key trends in the dataset are explored through visualizations, highlighting changes in the total homeless population over time, the distribution across age groups and genders, and the variation in both the number and percentage of the chronic homeless population.
 
@@
 
-# This code draws on concepts from Alexander (2023)
 # Load ggplot2 for plotting
@@
 #| warning: false
-#| label: fig-age-distribution
-#| fig-cap: "Age Group Distribution of Homeless Population in Toronto (2018-2024)"
+#| label: fig-age-distribution-sidebyside
+#| fig-cap: "Homeless Population by Age Group in Toronto"
+#| fig-subcap: ["Age Group Distribution (2018-2024)", "Trends in Age Group Proportions Over Time"]
+#| layout-ncol: 2
 
@@
 # Reshape data for plotting
-# Generated by ChatGPT
 total_data_long <- tidyr::pivot_longer(total_data, 
@@
 
+# Modify age group labels for simplicity
+total_data_long <- total_data_long %>%
+  mutate(Age_Group = case_when(
+    Age_Group == "Age_Under_16" ~ "Under 16",
+    Age_Group == "Age_16_24" ~ "16-24",
+    Age_Group == "Age_25_34" ~ "25-34",
+    Age_Group == "Age_35_44" ~ "35-44",
+    Age_Group == "Age_45_54" ~ "45-54",
+    Age_Group == "Age_55_64" ~ "55-64",
+    Age_Group == "Age_65_Over" ~ "65 and over",
+    TRUE ~ Age_Group
+  ))
+
 # Calculate percentages
-# Generated by ChatGPT
+
 total_count <- sum(total_data_long$Count)
@@
 # Create a pie chart with percentage labels
-# This code draws on concepts from Alexander (2023)
 ggplot(total_data_long, aes(x = "", y = Count, fill = Age_Group)) +
@@
   theme(legend.position = "right") +
-  scale_fill_brewer(palette = "Set3")
+  labs(fill = "Age Group") + 
+  scale_fill_brewer(palette = "Set2")
+
+# Summarize data by year and age group
+yearly_data <- cleaned_shelter_data %>%
+  group_by(year) %>%
+  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
+            Age_16_24 = sum(Age_16_24, na.rm = TRUE),
+            Age_25_34 = sum(Age_25_34, na.rm = TRUE),
+            Age_35_44 = sum(Age_35_44, na.rm = TRUE),
+            Age_45_54 = sum(Age_45_54, na.rm = TRUE),
+            Age_55_64 = sum(Age_55_64, na.rm = TRUE),
+            Age_65_Over = sum(Age_65_Over, na.rm = TRUE))
+
+# Reshape the data for plotting
+yearly_data_long <- tidyr::pivot_longer(yearly_data, 
+                                        cols = starts_with("Age"), 
+                                        names_to = "Age_Group", 
+                                        values_to = "Count")
+
+# Modify age group labels for simplicity
+yearly_data_long <- yearly_data_long %>%
+  mutate(Age_Group = case_when(
+    Age_Group == "Age_Under_16" ~ "Under 16",
+    Age_Group == "Age_16_24" ~ "16-24",
+    Age_Group == "Age_25_34" ~ "25-34",
+    Age_Group == "Age_35_44" ~ "35-44",
+    Age_Group == "Age_45_54" ~ "45-54",
+    Age_Group == "Age_55_64" ~ "55-64",
+    Age_Group == "Age_65_Over" ~ "65 and over",
+    TRUE ~ Age_Group
+  ))
+
+# Calculate total homeless population per year and add percentage column
+yearly_data_long <- yearly_data_long %>%
+  group_by(year) %>%
+  mutate(Total_Count = sum(Count),
+         Percent = Count / Total_Count * 100)
+
+# Create a line chart showing the percentage of each age group over time without a title
+ggplot(yearly_data_long, aes(x = year, y = Percent, color = Age_Group, group = Age_Group)) +
+  geom_line(size = 1.2) +  
+  labs(x = "Year", y = "Percentage of Homeless Population", color = "Age Group") +  
+  scale_color_brewer(palette = "Set2") +  
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "right")
 
 ```
-@fig-age-distribution shows the percentage of Toronto's homeless population in each age group as a proportion of the total homeless population from 2018 to 2024.
-The largest age group is 35-44 years old, accounting for about 21\% of the total population, followed by the 25-34 age group (approximately 18\%), the 45-54 age group (approximately 17\%), and the 55-64 age group (approximately 14\%).
+
+@fig-age-distribution-sidebyside shows the percentage of Toronto's homeless population by age group from 2018 to 2024, along with changes in each group's share over time.
+Overall, the largest age group is 35-44 years old, accounting for about 21\% of the total population, followed by the 25-34 age group (approximately 18\%), the 45-54 age group (approximately 17\%), and the 55-64 age group (approximately 14\%).
 The under 16 and 16-24 age groups each account for 12\%.
@@
 #| warning: false
-#| label: fig-gender-distribution
-#| fig-cap: "Homeless Population by Gender in Toronto (2018-2024)"
-#| 
+#| label: fig-gender-distribution-sidebyside
+#| fig-cap: "Homeless Population by Gender in Toronto"
+#| fig-subcap: ["Gender Distribution (2018-2024)", "Trends in Gender Proportions Over Time"]
+#| layout-ncol: 2
+
 # Summarize data by year for different genders
-# This logic is similar to the previous graph of age group 
 gender_data <- cleaned_shelter_data %>%
@@
             Female = sum(Female_Count, na.rm = TRUE),
-            Transgender_Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE))  # Change 'Other' to 'Transgender/Non-binary'
+            Transgender_Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE))
 
@@
 total_population <- gender_data %>%
-  summarise(Male = sum(Male), Female = sum(Female), Transgender_Non_Binary = sum(Transgender_Non_Binary))  # Adjust for renamed column
+  summarise(Male = sum(Male), Female = sum(Female), Transgender_Non_Binary = sum(Transgender_Non_Binary))
 
@@
                                       values_to = "Total_Count") %>%
-  mutate(Gender = recode(Gender, "Transgender_Non_Binary" = "Transgender/Non-binary"))  # Replace underscore with /
+  mutate(Gender = recode(Gender, "Transgender_Non_Binary" = "Transgender/Non-binary"))
 
@@
 
-# Create a pie chart similar to the one used for age groups
-# This code is based on knowledge from Alexander (2023) and further refined using the RStudio Help documentation.
+# Create a pie chart showing the gender distribution
 ggplot(total_population_long, aes(x = "", y = Total_Count, fill = Gender)) +
@@
   theme(legend.position = "right") +
-  scale_fill_manual(values = c("Male" = "#7FB3D5", "Female" = "#F5B7B1", "Transgender/Non-binary" = "#D2B4DE"))  
+  scale_fill_brewer(palette = "Set2")
+
+# Reshape data for plotting gender proportions over time
+gender_data_long <- pivot_longer(gender_data, 
+                                 cols = c("Male", "Female", "Transgender_Non_Binary"), 
+                                 names_to = "Gender", 
+                                 values_to = "Count") %>%
+  mutate(Gender = recode(Gender, "Transgender_Non_Binary" = "Transgender/Non-binary"))
+
+# Calculate percentages per year
+gender_data_long <- gender_data_long %>%
+  group_by(year) %>%
+  mutate(Total_Count = sum(Count),
+         Percent = Count / Total_Count * 100)
+
+# Create a line chart to show gender distribution over time
+ggplot(gender_data_long, aes(x = year, y = Percent, color = Gender, group = Gender)) +
+  geom_line(size = 1.2) +  
+  labs(x = "Year", y = "Percentage of Homeless Population", color = "Gender") +  
+  scale_color_brewer(palette = "Set2") +  
+  theme_minimal() +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1),
+        legend.position = "right")
+
 ```
 
-@fig-gender-distribution presents the gender distribution of Toronto's homeless population from 2018 to 2024.
-During this period, males have consistently made up the largest proportion, accounting for approximately 61.8% of the total homeless population.
-Females make up about 36.8%, while non-binary individuals make up about 1.4%.
+@fig-gender-distribution-sidebyside shows the gender distribution of Toronto's homeless population from 2018 to 2024 and how it has changed over time.
+Males consistently represent the largest proportion, making up approximately 61.8% of the total homeless population, while females account for about 36.8%, and transgender or non-binary individuals make up around 1.4%.
+The percentages of males and transgender or non-binary individuals initially increase but begin to decline after 2021, with the opposite trend observed for females.
+However, these fluctuations are minor, staying within five percentage points.
 
@@
 
+# Generated by ChatGPT
 # Summarize data by year for Chronic and All Population
-# Generated by ChatGPT
 chronic_data <- cleaned_shelter_data %>%
@@
 
-The @fig-chronic-population displays the changes in the number and proportion of chronic and non-chronic homeless people in Toronto between 2018 and 2024.
+@fig-chronic-population displays the changes in the number and proportion of chronic and non-chronic homeless people in Toronto between 2018 and 2024.
 The number of chronically homeless has been growing over this time, with over 30,000 people in 2018, and by 2023, the number has gone to about 60,000, nearly doubling.
@@
 ## Overview of Homeless Trends (2018-2024)
-In @sec-data-results，trends in Toronto's homeless population from 2018 to 2024 are presented, focusing on key factors such as age, gender, and chronic versus non-chronic conditions.
-The homeless population fluctuates significantly, being significantly impacted in specific years such as 2020 and 2021[@fig-total-population], with males and the 35-44 age group making up the majority of the homeless population[@fig-age-distribution,@fig-gender-distribution], and chronic homelessness showing an increasing trend[@fig-chronic-population].
+@sec-data-results presents trends in Toronto's homeless population from 2018 to 2024, focusing on key factors such as age, gender, and chronic versus non-chronic conditions.
+The homeless population fluctuates greatly, with notable impacts in years like 2020 and 2021 (@fig-total-population), with males and the 35-44 age group making up the majority of the homeless population (@fig-age-distribution-sidebyside, @fig-gender-distribution-sidebyside), and chronic homelessness showing an increasing trend (@fig-chronic-population).
 
 ## Impact of COVID-19 on Homelessness
-The homeless population declined significantly in 2020 and 2021, likely due to COVID-19.
-To meet social distancing requirements, the Toronto government reduced shelter capacity and opened temporary shelters, including additional spaces in hotels and motels[@may2023scan].
+The homeless population declined in 2020 and 2021, likely due to COVID-19.
+To meet social distancing requirements, the Toronto government reduced shelter capacity and opened temporary shelters, including additional spaces in hotels and motels [@may2023scan].
 These actions may explain the drop during these years.
@@
 ## Demographic and Chronic Homelessness Insights
-An analysis of age, gender, and chronic homelessness provides key insights into Toronto's homeless population.
-Homelessness is concentrated among working-age adults, especially those aged 35-44 and 25-34, likely due to challenges with employment or housing stability.
-In terms of gender, males consistently make up the majority, while non-binary individuals account for only 1.4%.
-This suggests shelters should consider different designs for men and women, while also addressing the needs of non-binary individuals, despite their smaller numbers.
-The rise in chronic homelessness suggests that existing measures are not enough to help people exit homelessness permanently.
+
+Analysing age, gender and chronic homelessness helps to understand Toronto's homeless population.
+Homelessness is concentrated among working-age adults, particularly those aged 35-44 and 25-34, likely due to challenges with employment or housing stability.
+The sharp decline in the under-16 group during the pandemic may reflect government support for youth, but the subsequent increase underscores the need for sustained policies.
+In terms of gender, men remain the majority, with only 1.4% of people being transgender or non-binary.
+This suggests that shelters should design facilities to meet the different needs of men and women, while also accommodating transgender or non-binary people.
+The increase in the number of chronically homeless people highlights the inadequacy of current interventions to help people escape homelessness in the long term, and signals a worsening situation without further intervention.
 
@@
 The database used only includes people who use City of Toronto-funded overnight shelter services and fails to reflect people who spend the night outdoors or use other homeless services.
-According to the most recent Street Needs Assessment, approximately 18% of the homeless population is not included in the data[@torontosheltersystem].
+According to the most recent Street Needs Assessment, approximately 18% of the homeless population is not included in the data [@torontosheltersystem].
 

### 2024-09-26 paper/paper.qmd
add a reference

@@
 date-format: long
-abstract: "This paper explores Toronto’s homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness trends.
-The data reveal a decline during the pandemic, followed by a rebound, with males and individuals aged 35-44 making up the majority.
-The number of chronically homeless also increased significantly.
-These findings highlight the need for targeted interventions to address chronic homelessness and improve housing policies."
+abstract: "Toronto’s homeless population experienced changes between 2018 and 2024, with key trends in age, gender, and chronic homelessness.
+Using data from the Toronto Shelter System, this paper examines these trends and the effects of the COVID-19 pandemic.
+The results show that males aged 35-44 are the largest demographic, and the number of chronically homeless individuals has increased.
+Understanding these dynamics is essential for developing more effective policies to address homelessness and improve long-term housing stability."
 format: pdf
@@
 #| message: false
+#| 
 #### Workspace setup ####
@@
 library(tidyr)
+library(knitr)
+
 ```
@@
 Graphs and related explanations are provided.
-@sec-discussion further analyses the information presented in the graphs.
+@sec-discussion further analyses the information provided in the figures and describes the weaknesses of the study.
 
@@
 Unneeded variables are removed and renamed using `dplyr` [@dplyr] and `tidyr` [@tidyr], while graphs are plotted with `ggplot2` [@ggplot2].
+The `knitr` [@knitr] package is used to generate the final PDF report.
 
@@
 @fig-total-population illustrates the fluctuation in Toronto's homeless population from 2018 to 2024.
-The chart shows cyclical rises and falls, with more pronounced declines around 2020 and 2021, followed by a steady increase.The population reaches its highest point in 2024.
+The chart shows cyclical rises and falls, with more pronounced declines around 2020 and 2021, followed by a steady increase.
+The population reaches its highest point in 2024.
 Throughout this period, the homeless population varies between approximately 7,500 and 11,000 individuals.
@@
 The number of chronically homeless has been growing over this time, with over 30,000 people in 2018, and by 2023, the number has gone to about 60,000, nearly doubling.
-the slight drop in numbers in 2024 is due to the fact that the statistics were last updated on September 17, 2024, and it is projected that by the end of the year, the number will have exceeded the 2023 one.
+The slight drop in numbers in 2024 is due to the fact that the statistics were last updated on September 17, 2024, and it is projected that by the end of the year, the number will have exceeded the 2023 one.
 Similarly, the percentage of chronically homeless is growing every year, from 29.7% in 2019 to 63.7% in 2024.

### 2024-09-26 paper/paper.qmd
change the subtitle

@@
 title: "Trends and Challenges in Toronto’s Homeless Population (2018-2024)"
-subtitle: "A Focus on Demographics and Chronic Homelessness"
+subtitle: "Middle-Aged Males Leading the Homeless Population with Continued Growth in Chronic Homelessness"
 author: 

### 2024-09-26 scripts/01-download_data.R

@@ -33,4 +33,5 @@ shelter_system_statistics
 
 #### Save data ####
 
-write_csv(shelter_system_statistics, "/Users/liz/Downloads/starter_folder-main/data/raw_data/raw_data.csv")
+write_csv(shelter_system_statistics, here::here("data", "raw_data", "raw_data.csv"))
+

### 2024-09-26 scripts/02-data_cleaning.R

@@ -12,7 +12,7 @@
 library(tidyverse)
 
 # Read the data
-cleaned_shelter_data <- read_csv("/Users/liz/Downloads/starter_folder-main/data/raw_data/raw_data.csv") %>%
+cleaned_shelter_data <- read_csv(here::here("data", "raw_data", "raw_data.csv"))
   
   # Filter data to keep only 'All Population' and 'Chronic' rows
   filter(population_group %in% c('All Population', 'Chronic')) %>%
@@ -38,4 +38,5 @@ cleaned_shelter_data <- read_csv("/Users/liz/Downloads/starter_folder-main/data/
     Transgender_Non_Binary_Count = gender_transgender.non.binary_or_two_spirit)
 
 #### Save data ####
-write_csv(cleaned_shelter_data, "/Users/liz/Downloads/starter_folder-main/data/analysis_data/analysis_data.csv")
+  write_csv(cleaned_shelter_data, here::here("data", "analysis_data", "analysis_data.csv"))
+  

### 2024-09-26 scripts/03-test_data.R

@@ -12,7 +12,7 @@ library(tidyverse)
 
 #### Test data ####
 # Load the dataset
-simulated_data <- read.csv("/Users/liz/Downloads/starter_folder-main/data/raw_data/simulated_shelter_data.csv")
+simulated_data <- read_csv(here::here("data", "raw_data", "simulated_shelter_data.csv"))
 
 # Check the structure of the dataset
 # Generated by ChatGPT

### 2024-09-26 scripts/00-simulate_data.R
Change the way to simulate data

@@ -7,41 +7,50 @@
 # Pre-requisites: Install the tidyverse (Wickham et al. 2019) package.
 # Any other information needed? None
 
-#### Workspace setup ####
+#### Simulate data ####
 library(tidyverse)
 
-
-#### Simulate data ####
 # Set random seed to ensure reproducibility
 set.seed(500)
 
-# Simulate a date column from January 2018 to August 2024, monthly
-# Generated by ChatGPT
+# Simulate a date column from January 2018 to August 2024, formatted as "Mon-YY"
 dates <- seq(as.Date("2018-01-01"), as.Date("2024-08-01"), by = "month")
+formatted_dates <- format(dates, "%b-%y")
 
 # Simulate population groups
-population_groups <- c("Chronic", "All populations")
+population_groups <- c("All Population", "Chronic")
 
-# Generate random homeless counts
-homeless_count <- sample(1000:3000, length(dates) * length(population_groups), replace = TRUE)
+# Generate random homeless counts, ensuring All Population > Chronic
+all_population_count <- sample(3000:5000, length(dates), replace = TRUE)
+chronic_population_count <- sample(1000:2000, length(dates), replace = TRUE)
+homeless_count <- c(rbind(all_population_count, chronic_population_count))
 
-# Generate random age group counts
-age_under_16 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
-age_16_24 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
-age_25_34 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
-age_35_44 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
-age_45_54 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
-age_55_64 <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
-age_65_over <- sample(100:500, length(dates) * length(population_groups), replace = TRUE)
+# Function to distribute a total count into proportional parts
+distribute_proportionally <- function(total, n) {
+  proportions <- runif(n) # Generate random proportions
+  proportions <- proportions / sum(proportions) # Normalize to sum to 1
+  round(total * proportions) # Scale to total and round
+}
 
-# Generate random gender counts
[…]

### 2024-09-26 scripts/02-data_cleaning.R
Changing the way files are loaded

@@ -12,7 +12,8 @@
 library(tidyverse)
 
 # Read the data
-cleaned_shelter_data <- read_csv(here::here("data", "raw_data", "raw_data.csv"))
+cleaned_shelter_data <- read_csv(here::here("data", "raw_data", "raw_data.csv")) %>%
+  
   
   # Filter data to keep only 'All Population' and 'Chronic' rows
   filter(population_group %in% c('All Population', 'Chronic')) %>%

### 2024-09-27 paper/paper.qmd
Final commit

@@
 In addition to being a socio-economic issue, homelessness intersects with public health and social justice [@healthhomelessness].
-Understanding the trends and composition of the homeless population is critical to effective policymaking.
-However, existing data often lack detailed categorization, hindering a full understanding of the needs of specific groups.
-This study seeks to fill this gap.
+However, the existing data often lacks detailed classification, preventing a comprehensive understanding of the needs of specific groups.
+The present study seeks to fill this gap by analyzing the share and trends of different groups in the homeless population.
 
-Using the "Toronto Shelter System Flows" dataset form Toronto Open Data Platform [@torontosheltersystem], this paper examines trends in Toronto's homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness.
-Our analysis reveals a decline during the pandemic, followed by a rebound, with males and the 35-44 age group comprising the majority.
-The number of chronically homeless people continues to grow, providing important insights for policymakers.
+Using the "Toronto Shelter System Flows" dataset from the Toronto Open Data Platform [@torontosheltersystem], this paper examines trends in Toronto's homeless population from 2018 to 2024, focusing on age, gender, and chronic homelessness.
+Our analyses show that homelessness declined during the pandemic and then rebounded.
+Among all homeless people, males and the 35-44 age group make up the majority, and the number of chronically homeless people continues to grow.
+These results provide important insights for policymakers.
 
-In this essay, @sec-data-overview explains the background and necessity of using this dataset, followed by an explanation of the variables mentioned and the methods used.
+In this essay, @sec-data-overview explains the background and necessity for using the dataset, followed by an explanation of the dataset's measurements.
 @sec-data-results shows the changes in the number of homeless individuals, along with the proportions and trends over time for each age group, gender, and chronic homelessness.
@@
 It covers data from 2018 to September 2024, with the homeless count based on shelter admission records, including demographic information such as age and gender.
-The dataset also provides data on specific groups, including chronic homeless individuals, refugees, youth, single adults, and families.
+The dataset also provides data on specific groups, including chronically homeless individuals, refugees, youth, single adults, and families.
 The measurements are collected through the Shelter Management Information System (SMIS) and are updated monthly to ensure that trends in the homeless population are accurately and timely reflected [@torontosheltersystem].
@@
 @fig-gender-distribution-sidebyside shows the gender distribution of Toronto's homeless population from 2018 to 2024 and how it has changed over time.
-Males consistently represent the largest proportion, making up approximately 61.8% of the total homeless population, while females account for about 36.8%, and transgender or non-binary individuals make up around 1.4%.
+Males consistently represent the largest proportion, making up approximately 61.8% of the total homeless population, while females account for about 36.8%, and transgender or non-binary individuals makeup around 1.4%.
 The percentages of males and transgender or non-binary individuals initially increase but begin to decline after 2021, with the opposite trend observed for females.
@@
 Similarly, the percentage of chronically homeless is growing every year, from 29.7% in 2019 to 63.7% in 2024.
-Note that in 2019 to 2020 and 2023 to 2024, the rate grows faster, by about 10 percent.
+It should be noted that this percentage grows faster at about 10 percent between 2019 to 2020 and 2023 to 2024.
 
@@
 
-Analysing age, gender and chronic homelessness helps to understand Toronto's homeless population.
+Analyzing age, gender and chronic homelessness helps to understand Toronto's homeless population.
 Homelessness is concentrated among working-age adults, particularly those aged 35-44 and 25-34, likely due to challenges with employment or housing stability.
@@
 This suggests that shelters should design facilities to meet the different needs of men and women, while also accommodating transgender or non-binary people.
-The increase in the number of chronically homeless people highlights the inadequacy of current interventions to help people escape homelessness in the long term, and signals a worsening situation without further intervention.
+The increase in the number of chronically homeless people highlights the inadequacy of current interventions to help people escape homelessness in the long term and signals a worsening situation without further intervention.
 

### 2024-09-27 paper/paper.qmd
Final commit

@@
 
-Analyzing age, gender and chronic homelessness helps to understand Toronto's homeless population.
-Homelessness is concentrated among working-age adults, particularly those aged 35-44 and 25-34, likely due to challenges with employment or housing stability.
-The sharp decline in the under-16 group during the pandemic may reflect government support for youth, but the subsequent increase underscores the need for sustained policies.
-In terms of gender, men remain the majority, with only 1.4% of people being transgender or non-binary.
-This suggests that shelters should design facilities to meet the different needs of men and women, while also accommodating transgender or non-binary people.
-The increase in the number of chronically homeless people highlights the inadequacy of current interventions to help people escape homelessness in the long term and signals a worsening situation without further intervention.
+Analyzing age, gender and chronic homelessness provides insight into Toronto's homeless population.
+Homelessness is concentrated among working-age adults, particularly the 35-44 and 25-34-year-olds, which may be due to challenges they face with employment or housing stability.
+During the pandemic, there was a sharp fall in homelessness among the under-16s group, which may reflect government support for young people during the pandemic.
+However, subsequent increases highlight the need for sustained policies.
+
+In terms of gender, males remain in the majority (61.8\%) and only 1.4\% are transgender or non-binary, with little fluctuation in gender breakdown.
+In the long term, shelters should build facilities that are targeted to the male/female ratio.
+At the same time, the needs of transgender and non-binary people cannot be ignored, even if they make up only a small percentage of the population.
+
+The increase in the number of chronically homeless people is largely due to the continued rise in rents and house prices, which are far beyond the ability of many low-income residents to pay, leaving them without the means to maintain stable accommodation [@whitzman2023human].
+The rise in the proportion of people who are chronically homeless means that current interventions are not sufficient to help people out of homelessness and that the underlying issues need to be further addressed.
 

### 2024-09-27 scripts/00-simulate_data.R
Final commit

@@ -67,6 +67,3 @@ simulated_data <- data.frame(
 
 # Save the simulated data to the specified path
 write_csv(simulated_data, here::here("data", "raw_data", "simulated_shelter_data.csv"))
-
-
-

### 2024-09-27 scripts/01-download_data.R

@@ -34,4 +34,3 @@ shelter_system_statistics
 #### Save data ####
 
 write_csv(shelter_system_statistics, here::here("data", "raw_data", "raw_data.csv"))
-

### 2024-09-27 scripts/02-data_cleaning.R

@@ -1,6 +1,6 @@
 #### Preamble ####
-# Purpose: Cleans the raw dataset obtained from the 
-#"Toronto Shelter System Flow" dataset in the file "01-download_data.R".
+# Purpose: Cleans the raw dataset obtained from the
+# "Toronto Shelter System Flow" dataset in the file "01-download_data.R".
 # Author: Jianing Li
 # Date: September 23, 2024
 # Contact: lijianing.li@mail.utoronto.ca
@@ -13,15 +13,13 @@ library(tidyverse)
 
 # Read the data
 cleaned_shelter_data <- read_csv(here::here("data", "raw_data", "raw_data.csv")) %>%
-  
-  
   # Filter data to keep only 'All Population' and 'Chronic' rows
-  filter(population_group %in% c('All Population', 'Chronic')) %>%
-  
+  filter(population_group %in% c("All Population", "Chronic")) %>%
   # Remove unnecessary columns
-  select(-returned_from_housing, -returned_to_shelter, -newly_identified, 
-         -moved_to_housing, -became_inactive, -population_group_percentage, -X_id) %>%
-  
+  select(
+    -returned_from_housing, -returned_to_shelter, -newly_identified,
+    -moved_to_housing, -became_inactive, -population_group_percentage, -X_id
+  ) %>%
   # Rename columns
   rename(
     Date = date.mmm.yy.,
@@ -36,8 +34,8 @@ cleaned_shelter_data <- read_csv(here::here("data", "raw_data", "raw_data.csv"))
     Age_65_Over = age65over,
     Male_Count = gender_male,
     Female_Count = gender_female,
-    Transgender_Non_Binary_Count = gender_transgender.non.binary_or_two_spirit)
+    Transgender_Non_Binary_Count = gender_transgender.non.binary_or_two_spirit
+  )
 
 #### Save data ####
-  write_csv(cleaned_shelter_data, here::here("data", "analysis_data", "analysis_data.csv"))
-  
+write_csv(cleaned_shelter_data, here::here("data", "analysis_data", "analysis_data.csv"))

### 2024-09-27 scripts/03-test_data.R

@@ -94,5 +94,3 @@ if (nrow(duplicates) == 0) {
 } else {
   print("There are duplicate rows in the dataset.")
 }
-
-

### 2024-09-27 paper/paper.qmd
Final commit

@@
 library(knitr)
-
+library(styler)
 ```
@@
 All processes are performed through the `R` language [@citeR].
-Data is simulated, tested, and cleaned using the `tidyverse` [@tidyverse] packages, which also facilitate downloading data through `opendatatoronto` [@citeopendatatorontoR].
-Unneeded variables are removed and renamed using `dplyr` [@dplyr] and `tidyr` [@tidyr], while graphs are plotted with `ggplot2` [@ggplot2].
-The `knitr` [@knitr] package is used to generate the final PDF report.
+Data is simulated, tested, and cleaned using the `tidyverse` [@tidyverse] packages, which also facilitate downloading data through `opendatatoronto` [@citeopendatatorontoR] .
+Unneeded variables are removed and renamed using `dplyr` [@dplyr] and `tidyr` [@tidyr] packages, while graphs are plotted with `ggplot2` [@ggplot2].
+Code is formatted using `styler` [@styler], and the final PDF report is generated with `knitr` [@knitr] package.
+The workflow and code are based on guidelines from @tellingstorieswithdata.
 
@@
 # Loading the Cleaned Dataset #
-# Generated by ChatGPT
 cleaned_shelter_data <- read_csv(here::here("data", "analysis_data", "analysis_data.csv"))
 
-# Generated by ChatGPT
-cleaned_shelter_data$Date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format="%d-%b-%y")
+# This code was developed with assistance from ChatGPT.
+# Convert date strings and extract year
+cleaned_shelter_data$Date <- as.Date(paste0("01-", cleaned_shelter_data$Date), format = "%d-%b-%y")
 cleaned_shelter_data$year <- as.numeric(format(cleaned_shelter_data$Date, "%Y"))
-
 ```
@@
 # Filter to include only the "All Population" group
+# This code was developed with assistance from ChatGPT.
 total_population_data <- subset(cleaned_shelter_data, Population_Group == "All Population")
@@
 # Load ggplot2 for plotting
+# This code is based on Alexander (2023).
 ggplot(total_population_data, aes(x = Date, y = Homeless_Count)) +
   geom_line(color = "blue", linewidth = 1.5) +
-  labs(x = "Date",
-       y = "Homeless Population Count") +
+  labs(
+    x = "Date",
+    y = "Homeless Population Count"
+  ) +
   scale_x_date(date_labels = "%Y", date_breaks = "1 year") +
@@
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
 ```
@@
 # Summarize data for all years (total homeless population by age group)
-# Generated by ChatGPT
+# This code was developed with assistance from ChatGPT.
 total_data <- cleaned_shelter_data %>%
-  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
+  summarise(
+    Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
     Age_16_24 = sum(Age_16_24, na.rm = TRUE),
@@
     Age_55_64 = sum(Age_55_64, na.rm = TRUE),
-            Age_65_Over = sum(Age_65_Over, na.rm = TRUE))
+    Age_65_Over = sum(Age_65_Over, na.rm = TRUE)
+  )
 
@@
   names_to = "Age_Group",
-                                       values_to = "Count")
+  values_to = "Count"
+)
 
@@
   geom_text(aes(label = paste0(Percent, "%")),
-            position = position_stack(vjust = 0.5), size = 4) +
+    position = position_stack(vjust = 0.5), size = 4
+  ) +
   theme_void() +
@@
   group_by(year) %>%
-  summarise(Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
+  summarise(
+    Age_Under_16 = sum(Age_Under_16, na.rm = TRUE),
     Age_16_24 = sum(Age_16_24, na.rm = TRUE),
@@
   names_to = "Age_Group",
-                                        values_to = "Count")
+  values_to = "Count"
+)
 
@@
   group_by(year) %>%
-  mutate(Total_Count = sum(Count),
-         Percent = Count / Total_Count * 100)
+  mutate(
+    Total_Count = sum(Count),
+    Percent = Count / Total_Count * 100
+  )
 
@@
   theme_minimal() +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1),
-        legend.position = "right")
-
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    legend.position = "right"
+  )
 ```
@@
 
+# This code was developed with assistance from ChatGPT.
 # Summarize data by year for different genders
@@
   group_by(year) %>%
-  summarise(Male = sum(Male_Count, na.rm = TRUE),
+  summarise(
+    Male = sum(Male_Count, na.rm = TRUE),
     Female = sum(Female_Count, na.rm = TRUE),
-            Transgender_Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE))
+    Transgender_Non_Binary = sum(Transgender_Non_Binary_Count, na.rm = TRUE)
+  )
 
@@
   names_to = "Gender",
-                                      values_to = "Total_Count") %>%
+  values_to = "Total_Count"
+) %>%
   mutate(Gender = recode(Gender, "Transgender_Non_Binary" = "Transgender/Non-binary"))
@@
   geom_text(aes(label = paste0(Percent, "%")),
-            position = position_stack(vjust = 0.5), size = 4, fontface = "bold", color = "gray30") +  
+    position = position_stack(vjust = 0.5), size = 4, fontface = "bold", color = "gray30"
+  ) +
   theme_void() +
@@
   names_to = "Gender",
-                                 values_to = "Count") %>%
+  values_to = "Count"
+) %>%
   mutate(Gender = recode(Gender, "Transgender_Non_Binary" = "Transgender/Non-binary"))
@@
 
-# Generated by ChatGPT
+# This code was developed with assistance from ChatGPT.
 # Summarize data by year for Chronic and All Population
 chronic_data <- cleaned_shelter_data %>%
-  filter(Population_Group == 'Chronic') %>%
+  filter(Population_Group == "Chronic") %>%
   group_by(year) %>%
@@
 all_population_data <- cleaned_shelter_data %>%
-  filter(Population_Group == 'All Population') %>%
+  filter(Population_Group == "All Population") %>%
   group_by(year) %>%
@@
 non_chronic_data$homeless_count <- non_chronic_data$homeless_count - chronic_data$homeless_count
-non_chronic_data$group <- 'Non-Chronic'
+non_chronic_data$group <- "Non-Chronic"
 
 # Add Chronic to the dataset
-chronic_data$group <- 'Chronic'
+chronic_data$group <- "Chronic"
 combined_data <- rbind(chronic_data, non_chronic_data) # Combine data
@@
   geom_bar(stat = "identity", position = "stack") +
-  geom_text(data = proportions, aes(x = year, y = homeless_count_chronic, label = paste0(percentage, "%")),
-            vjust = 1.5, color = "white", size = 3) +  # Add percentage labels in white color
+  geom_text(
+    data = proportions, aes(x = year, y = homeless_count_chronic, label = paste0(percentage, "%")),
+    vjust = 1.5, color = "white", size = 3
+  ) + # Add percentage labels in white color
   labs(x = "Year", y = "Homeless Population Count", fill = "Group") +
@@
   scale_x_continuous(breaks = seq(min(combined_data$year), max(combined_data$year), by = 1))
-
 ```

### 2024-09-27 paper/paper.qmd
Final commit

@@
 
-# Introduction
+# Introduction {#sec-introduction}
 
@@
 
-## Overview of Homeless Trends (2018-2024)
+## Overview of Homeless Trends (2018-2024) {#sec-discussion-overview}
+
 @sec-data-results presents trends in Toronto's homeless population from 2018 to 2024, focusing on key factors such as age, gender, and chronic versus non-chronic conditions.
@@
 
-## Impact of COVID-19 on Homelessness
+## Impact of COVID-19 on Homelessness {#sec-discussion-COVID}
+
 The homeless population declined in 2020 and 2021, likely due to COVID-19.
@@
 
-## Demographic and Chronic Homelessness Insights
+## Demographic and Chronic Homelessness Insights {#sec-discussion-insight}
 
@@
 
-## Weaknesses and next steps
-A limitation of this analysis is that the data analyzed does not reflect the entire Toronto homeless population.
-The database used only includes people who use City of Toronto-funded overnight shelter services and fails to reflect people who spend the night outdoors or use other homeless services.
-According to the most recent Street Needs Assessment, approximately 18% of the homeless population is not included in the data [@torontosheltersystem].
+## Weaknesses and next steps {#sec-discussion-weakness}
 
-Future directions for improvement should include expanding the data scope of the analysis to include people who spend the night outdoors and use shelters that are not funded by the Government of Toronto, in order to provide a more complete picture of homelessness in Toronto.
-This will help fill data gaps and support more effective policy decisions.
+A limitation of this analysis is that the dataset used does not fully capture the overall status of homelessness in Toronto.
+It only includes individuals who utilize City of Toronto-funded overnight shelter services, excluding those who spend the night outdoors or use other homeless services.
+These excluded groups represent approximately 18\% of the homeless population [@torontosheltersystem].
+Future studies could aim to collect more comprehensive data by including these populations.
+
+Additionally, the variables analyzed in this article were limited to basic demographic information such as gender, age, and chronic homelessness status.
+Future analyses could incorporate more complex variables, such as the influence of different socioeconomic factors (e.g., income, education level, employment status) on homelessness.
+By examining interactions between these variables, it may be possible to uncover deeper insights into the root causes of homelessness.
 
@@
 
-# References
+# References {#sec-references}
